\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-08-09 article.tex
Minor re-wording in intro
Added text to the approach section

% Use the following packages
\usepackage[utf8]{inputenc}     % Support for UTF-8
\usepackage{dcolumn}            % Align table columns on decimal point
\usepackage{graphicx}           % Include graphics
\usepackage{asymptote}          % Vector graphics language
\usepackage{listings}           % Pretty source code listings
\usepackage{url}                % Handle URLs better

@@

  In this article, therefore, we analyze hand techniques in patterns Chon-Ji
  to Juche using tags and report our findings of a left arm bias.

@@

@@

% the approach taken to register and investigate the dataset

% added tags
%   give an overview over (groups of) tags, see movements_with_tags.txt
%     Group of tags
%     Groups of techniques {blocks, strikes, thrusts, punches}
%       height
%       weapon
%       type etc.
%   show an example (chon-ji movement no. 1, for instance)
% divided each pattern into its own text file (./patterns/*)
% modelled the project in the database (./models)
%   explain all attributes etc.
% made a ruby script to parse the text files (link to bootstrap.rb ?)
%   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
%   saving the data into an sqlite3 database for analysis
%

% Tagging
%   tagging (how is tagging used? what is its role?)
%   connect set theory to tagging? how is it applied to tags and tagging?

% hva forholder jeg meg til ved utvetydigheter (15-binds vs. *kondenserte*)
% vurderinger på teknikker
% hvorfor er tekniker gruppert slik de er?

>>>>

% Use the following packages
\usepackage[utf8]{inputenc}     % Support for UTF-8
\usepackage{dcolumn}            % Align table columns on decimal point
\usepackage{graphicx}           % Include graphics
\usepackage{asymptote}          % Vector graphics language
\usepackage{listings}           % Pretty source code listings
\usepackage{url}                % Handle URLs better
\usepackage{amsmath}            % Extend mathematical typesetting

@@

  In this article, therefore, we analyze hand techniques in patterns Chon-Ji
  to Juche using tags and then report our findings of a left arm bias.

@@

% TODO: vurderinger på teknikker, se notater i wikien

@@

  Each pattern movement is tagged on the basis of their English description
  from the condensed encyclopedia. In addition, suitable tags is attached to
  the dataset while performing the pattern to add necessary detail.

  The first movement in Chon-Ji, for instance, is to ``[m]ove the left foot to
  B, forming a left walking stance toward B while executing a low block to B
  with the left forearm\cite{cyclo:vol1}.'' Removing the verbose parts of the
  description we're left with:

  \[
    \{left \: walking \: stance, \: low \: block, \: left \: forearm\}
  \]

  Converting the above to tags gives us:

  \begin{align*}
    \{walking \: stance, \: left \: stance, \: low \: technique, \\
    left \: technique, \: block, \: forearm, \: outer \: forearm, \\
    normal \: motion\}
  \end{align*}

  Information about the stance type is presented first, followed by stance
  side (left, right or none where applicable --- ie. sitting stance, technique
  height (low, middle, high), technique side (left arm or right arm, can also
  be both), direction of the technique (when needed), primary technique type
  (attack, block, kick), technique group (punch, strike, thrust), tool group
  (forearm, knife hand, finger etc.), tool (inner forearm, outer forearm,
  double finger etc.), and finally motion type (normal motion, slow motion,
  consecutive motion and so on).

  Tagging movements in such a formalized manner enables us to retrieve the
  data we're interested in, using concepts from set theory.

% modelled the project in the database (./models)
%   explain all attributes etc.
% made a ruby script to parse the text files (link to bootstrap.rb ?)
%   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
%   saving the data into an sqlite3 database for analysis
%
